Fluid structure interaction with ETVF

### 2021-07-05 manuscript/paper.tex
Fix substepping and update examples.

@@

@@

In this example the elastic plate is placed at the end. Which gets
impacted due to the moving fluid. Further information can be found at
section 3.2 of \cite{liu2013numerical}

>>>>

\citet{sun2019fully} couples MPS and BPM model to simulate FSI. He models both
elastic dam break and flow over an elastic obstacle.

@@

Taken from \citet{sun2019fully}.

@@

In this example the elastic plate is placed at the end. Which gets
impacted due to the moving fluid. Further information can be found at
section 3.2 of \cite{liu2013numerical}, \citet{sun2019fully}.
